Re-examining cross-cultural similarity judgements using lexical co-occurrence

### 2023-01-13 code/4_paper/manuscript/manuscript.Rmd
added ICC

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")

@@

>>>>

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("irr")

@@

# Appendix
## 1. ICC of item variability and participant variability 
```{r item variability, include = F}
df.icc_item_full <- df_main_analysis %>% 
  select(subject, triad, responses_theme) %>%
  pivot_wider(names_from = subject, values_from = responses_theme)

icc_item_full <- icc(df.icc_item_full %>% select(-triad), model = "twoway", type = "consistency", unit = "single")$value

df.icc_item <- df_main_analysis %>% 
  select(subject, triad, responses_theme, country) %>%
  pivot_wider(names_from = subject, values_from = responses_theme)

#unsure if type should be consistency or agreement
df.icc_item_US <- df.icc_item %>% 
  filter(country == "US") %>%
  select_if(~ !any(is.na(.))) %>%
  select(-country, -triad)

icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "consistency", unit = "single")$value

#unsure if type should be consistency or agreement
df.icc_item_VN <- df.icc_item %>% 
  filter(country == "Vietnam") %>%
  select_if(~ !any(is.na(.))) %>%
  select(-country, -triad)

icc_item_VN <- icc(df.icc_item_VN, model = "twoway", type = "consistency", unit = "single")$value

#unsure if type should be consistency or agreement
df.icc_item_CN <- df.icc_item %>% 
  filter(country == "China") %>%
  select_if(~ !any(is.na(.))) %>%
  select(-country, -triad)

icc_item_CN <- icc(df.icc_item_CN, model = "twoway", type = "consistency", unit = "single")$value
```

```{r participant variability, include = F}
df.icc_ppt_full <- df_main_analysis %>% 
  select(subject, triad, responses_theme) %>%
  pivot_wider(names_from = triad, values_from = responses_theme)

icc_ppt_full <- icc(df.icc_ppt_full %>% select(-subject), model = "twoway", type = "consistency", unit = "single")$value

df.icc_ppt <- df_main_analysis %>% 
  select(subject, triad, responses_theme, country) %>%
  pivot_wider(names_from = triad, values_from = responses_theme)

#unsure if type should be consistency or agreement
df.icc_ppt_US <- df.icc_ppt %>% 
  filter(country == "US") %>%
  select(-country, -subject)

icc_ppt_US <- icc(df.icc_ppt_US, model = "twoway", type = "consistency", unit = "single")$value

#unsure if type should be consistency or agreement
df.icc_ppt_VN <- df.icc_ppt %>% 
  filter(country == "Vietnam") %>%
  select(-country, -subject)

icc_ppt_VN <- icc(df.icc_ppt_VN, model = "twoway", type = "consistency", unit = "single")$value

#unsure if type should be consistency or agreement
df.icc_ppt_CN <- df.icc_ppt %>% 
  filter(country == "China") %>%
  select(-country, -subject)

icc_ppt_CN <- icc(df.icc_ppt_CN, model = "twoway", type = "consistency", unit = "single")$value
```

```{r}
icc_tbl <- data.frame(
  Country = c("US", "China", "Vietnam", "All"),
  Item_Variability_ICC = c(icc_item_US, icc_item_CN, icc_item_VN, icc_item_full), 
  Ppt_Variabiity_ICC = c(icc_ppt_US, icc_ppt_CN, icc_ppt_VN, icc_ppt_full)
)
kable(icc_tbl)
```

## 2. CCRR agreement
```{r load CCRR data}
df.ccrr <- read.csv("../../../data/replication/ccrr.csv") %>%
  filter(task_name == "TD") %>%
  select(subject, trial_info, resp) %>%
  rename(triad = trial_info) %>%
  mutate(response_theme = ifelse(resp == "FALSE", 1, 0)) %>%
  select(subject, triad, response_theme) %>%
  pivot_wider(names_from = subject, values_from = response_theme) %>%
  select(-triad)

df.ccrr %>%
    dplyr::group_by(triad, subject) %>%
    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
    dplyr::filter(n > 1L)

icc(df.ccrr, model = "twoway", type = "consistency", unit = "single")
```
